Leadership across cultures and contexts: an exploratory analysis

### 2020-06-18 leadership_across_cultures_contexts.Rmd
Changed methods coding to two versions

@garfield_evolutionary_2019 describe a database of ethnographic texts on leadership they assembled (https://doi.org/10.5281/zenodo.2541999) from the electronic Human Relations Area Files (eHRAF), a digital collection of ethnographies, subject-coded at the paragraph level following the Outline of Cultural Materials (OCM) coding scheme. This database used the 60-culture Probability Sample Files (PSF) subsample [@naroll_proposed_1967] to capture a wide sample of the ethnographic record of leadership across social contexts. We use the same database of `r nrow(all_data)` ethnographic paragraphs (termed text records) to code entirely new variables on the functions and qualities of leaders and the costs and benefits of leadership and followership.

We operationalized leader qualities and functions from the ethnographic text records in the database using an interative process based on multiple passes through many paragraphs, i.e., these operationalizations were not developed *a priori*. The final list of variables is given in Table S\@ref(tab:qualfuncvars) and KS and ZG coded the entire sample of `r nrow(all_data)` text records for the `r length(c(quality_vars, function_vars, leader_cost_vars, leader_benefit_vars, follower_benefit_vars, follower_cost_vars))` operationalized variables, which we henceforth refer to as leadership dimensions.

@@

See @garfield_evolutionary_2019 and the SI for additional details on the ethnographic sample.

@@

<!-- @garfield_evolutionary_2019 describe a database of ethnographic texts on leadership they assembled (https://doi.org/10.5281/zenodo.2541999) from the electronic Human Relations Area Files (eHRAF), a digital collection of ethnographies, subject-coded at the paragraph level following the Outline of Cultural Materials (OCM) coding scheme. We use the same database of `r nrow(all_data)` ethnographic paragraphs (termed text records) to code entirely new variables on the functions and qualities of leaders and the costs and benefits of leadership and followership. -->

<!-- The text records were extracted from the 60-culture Probability Sample Files (PSF) of the eHRAF [@naroll_proposed_1967]. The PSF, which comprises over `r trunc(sum(leader_cult['ehraf_pages'])/1000)`K pages of digitized text, aims to mitigate Galton's problem of cultural non-independence by randomly sampling of one culture with high quality ethnographic coverage from each of 60 culture regions. The database of text records was designed to capture a wide sample of the ethnographic record of leadership across social contexts and was built using an advanced search including 16 OCM codes related to leadership and seven key words describing leaders or followers. See @garfield_evolutionary_2019 for additional details on the ethnographic sample. -->

<!-- To operationalize leader qualities and functions from the ethnographic text records in the database, ZG first read a subset of text records and developed initial variable lists and operationalizations of the qualities and functions in those text records. KS then coded approximately half the `r nrow(all_data)` text records (in a random order) for the operationalized qualities, functions, cost, and benefits, while also creating new variables and operationalizations for additional qualities and functions encountered. After coding half of the random sample, KS and ZG revised the operational definitions to produce the final list of variables in Table S\@ref(tab:qualfuncvars). KS and ZG then coded the entire sample of `r nrow(all_data)` text records for the `r length(c(quality_vars, function_vars, leader_cost_vars, leader_benefit_vars, follower_benefit_vars, follower_cost_vars))` operationalized variables, which we henceforth refer to as leadership dimensions. -->

<!-- In contrast to the qualities and functions dimensions, operationalizations of the costs and benefits of leadership were developed *a priori* based on theoretical literature. For both followers and leaders, we coded evidence of costs paid or benefits received in the following categories: social status, reduced or increased risk of harm or conflict, social services, territory, mating, fitness, food resources, material resources, and other miscellaneous costs or benefits not captured by these categories (Table S\@ref(tab:costbenefitvars)). Some of the costs and benefits (e.g., mating) were similar to leader qualities (e.g., polygyny). The distinction is that costs and benefits were transactional whereas qualities were descriptive (e.g., leaders obtain wives vs. have wives). -->

<!-- ZG then created a measure of group context coded as: *residential subgroup*, which includes informal groups of co-residents, social groups, age-based groups, or performance groups; *kin group*, which includes lineages, phraties, and other kin-based organizations; *economic group*, which includes subsistence groups, market groups, and other groups with primarily economic goals; *military group*, which includes all groups related to inter-group conflict; *religious group*, which includes groups collected for spiritual or supernatural purpose; *political group (community)*, which includes political groups at the level of the community, i.e., the political leader can potentially interact directly with most community members such as most village headmen; or *political group (supracommunity)*, which includes political groups that encompass multiple residential communities, such as complex chiefdoms, regional political leaders, and kings or state-level leaders. ZG and KS coded all text records for group context. Finally, the sex of each leader was coded as male, female, both, or unknown. -->

@@

>>>>

@garfield_evolutionary_2019 describe a database of ethnographic texts on leadership they assembled (https://doi.org/10.5281/zenodo.2541999) from the electronic Human Relations Area Files (eHRAF), a digital collection of ethnographies, subject-coded at the paragraph level following the Outline of Cultural Materials (OCM) coding scheme. We use the same database of `r nrow(all_data)` ethnographic paragraphs (termed text records) to code entirely new variables on the functions and qualities of leaders and the costs and benefits of leadership and followership.

The text records were extracted from the 60-culture Probability Sample Files (PSF) of the eHRAF [@naroll_proposed_1967]. The PSF, which comprises over `r trunc(sum(leader_cult['ehraf_pages'])/1000)`K pages of digitized text, aims to mitigate Galton's problem of cultural non-independence by randomly sampling of one culture with high quality ethnographic coverage from each of 60 culture regions. The database of text records was designed to capture a wide sample of the ethnographic record of leadership across social contexts and was built using an advanced search including 16 OCM codes related to leadership and seven key words describing leaders or followers. See @garfield_evolutionary_2019 for additional details on the ethnographic sample.

To operationalize leader qualities and functions from the ethnographic text records in the database, ZG first read a subset of text records and developed initial variable lists and operationalizations of the qualities and functions in those text records. KS then coded approximately half the `r nrow(all_data)` text records (in a random order) for the operationalized qualities, functions, cost, and benefits, while also creating new variables and operationalizations for additional qualities and functions encountered. After coding half of the random sample, KS and ZG revised the operational definitions to produce the final list of variables in Table S\@ref(tab:qualfuncvars). KS and ZG then coded the entire sample of `r nrow(all_data)` text records for the `r length(c(quality_vars, function_vars, leader_cost_vars, leader_benefit_vars, follower_benefit_vars, follower_cost_vars))` operationalized variables, which we henceforth refer to as leadership dimensions.

@@

@@

<!-- SHORTENDED VERSION -->

<!-- @garfield_evolutionary_2019 describe a database of ethnographic texts on leadership they assembled (https://doi.org/10.5281/zenodo.2541999) from the electronic Human Relations Area Files (eHRAF), a digital collection of ethnographies, subject-coded at the paragraph level following the Outline of Cultural Materials (OCM) coding scheme. This database used the 60-culture Probability Sample Files (PSF) subsample [@naroll_proposed_1967] to capture a sample of the ethnographic record of leadership across diverse cultures and contexts. We use the same database of `r nrow(all_data)` ethnographic paragraphs (termed text records) to code entirely new variables on the functions and qualities of leaders and the costs and benefits of leadership and followership. -->

<!-- We operationalized leader qualities and functions from the ethnographic text records in the database using an interative process based on multiple passes through many paragraphs, i.e., these operationalizations were not developed *a priori*. The final list of variables is given in Table S\@ref(tab:qualfuncvars) and KS and ZG coded the entire sample of `r nrow(all_data)` text records for the `r length(c(quality_vars, function_vars, leader_cost_vars, leader_benefit_vars, follower_benefit_vars, follower_cost_vars))` operationalized variables, which we henceforth refer to as leadership dimensions. -->

<!-- In contrast to the qualities and functions dimensions, operationalizations of the costs and benefits of leadership were developed *a priori*. For both followers and leaders, we coded evidence of costs paid or benefits received in the following categories: social status, reduced or increased risk of harm or conflict, social services, territory, mating, fitness, food resources, material resources, and other miscellaneous costs or benefits not captured by these categories (Table S\@ref(tab:costbenefitvars)). Some of the costs and benefits (e.g., mating) were similar to leader qualities (e.g., polygyny). The distinction is that costs and benefits were transactional whereas qualities were descriptive (e.g., leaders obtain wives vs. have wives). -->

<!-- ZG and KS also coded all text records for group context coded as: *residential subgroup*, which includes informal groups of co-residents, social groups, age-based groups, or performance groups; *kin group*, which includes lineages, phraties, and other kin-based organizations; *economic group*, which includes subsistence groups, market groups, and other groups with primarily economic goals; *military group*, which includes all groups related to inter-group conflict; *religious group*, which includes groups collected for spiritual or supernatural purpose; *political group (community)*, which includes political groups at the level of the community, i.e., the political leader can potentially interact directly with most community members such as most village headmen; or *political group (supracommunity)*, which includes political groups that encompass multiple residential communities, such as complex chiefdoms, regional political leaders, and kings or state-level leaders. Finally, the sex of each leader was coded as male, female, both, or unknown. -->

@@

<!-- <!-- ADD OTHER TEXT FROM ORIGINAL SECTION TO SI ?? --> -->

<!-- See @garfield_evolutionary_2019 and the SI for additional details on the ethnographic sample. -->
